\appendix 
\chapter{Список сотрудников коллаборации ARGUS}
\label{sec:authors}
%   03/07/89 304222203  MEMBER NAME  ARGTITLE (TEX.S)    M  TEX
%
% This is an ARGUS title page with full author list / rev 91/6/17
%
% Use it with LaTeX
%
% The title of the paper should be provided in the \title{...} field.
%
%%%%%%%% layout of title page
\message{*** ARGUS title page, to be used with LaTeX ***}
\pagestyle{empty}
\setlength{\oddsidemargin}{0pt}
\setlength{\evensidemargin}{0pt}
\setlength{\marginparwidth}{2.4truecm}
\setlength{\marginparsep}{0pt}
\setlength{\topmargin}{0pt}
\setlength{\headheight}{0pt}
\setlength{\headsep}{0pt}
\setlength{\topskip}{0pt}
\setlength{\textheight}{24.7truecm}
\setlength{\textwidth}{16.4truecm}
%\setlength{\footheight}{12pt}
\setlength{\footskip}{24pt}
\renewcommand{\baselinestretch}{1.0}
\parskip = 4pt plus 0.10fill
%%%%%%%%% no page number
\let\thepage\relax
%%%%%%%%% formatting of paragraphs
\def\centerformat{%
    \pretolerance = 2000 \tolerance = 3000 \hbadness 500
    \parindent = 0pt \parskip = 0pt \catcode"0D = 5
    \rightskip = 20pt plus 1fill\leftskip  = 20pt plus 1fill
    \spaceskip = 0.35em \xspaceskip = 0.45em \parfillskip = 0pt
    \hyphenpenalty = 1000 \exhyphenpenalty = 1000}
%%%%%%%%% initial-name separation
\def\:{.\kern 2pt\relax}
%%%%%%%%% font definitions
\font\sixrm=cmr6
\font\egtrm=cmr8
%%
%%%%%%%%%
%%%%%%%%% TITLE
%%%%%%%%%
\def\title#1{{\centerformat{%
    \Large \bf
    #1\par}}%
    \vskip 2pt\vskip\parskip}
%%%%%%%%%
%%%%%%%%% AUTHORs' NAMES
%%%%%%%%%
\def\authors#1{{\centerformat{\rm #1\par}}}
%%%%%%%%%
%%%%%%%%% INSTITUTIONs' NAMES
%%%%%%%%%
\def\inst#1{{\centerformat{\it #1\par}}\vskip \parskip}
%%%%%%%%%
%%%%%%%%% special footnote macro
%%%%%%%%%
\newcount\fnnumber
\def\fn#1#2{\/%
    \expandafter\ifx\csname FnN#1\endcsname\relax%
    \global\advance\fnnumber 1%
    \expandafter\xdef\csname FnN#1\endcsname%
    {\the\fnnumber}%
    \insert\footins{\interlinepenalty=\interfootnotelinepenalty
    \leftskip=0pt\rightskip=0pt\parfillskip=0pt plus 1fill
    \spaceskip=2.5pt plus 1.5pt minus 1pt
    \xspaceskip=3pt plus 2pt minus 1pt
    \baselineskip = 0.8\normalbaselineskip \lineskip = \normallineskip
    \pretolerance=2000\tolerance=3000
    \hyphenpenalty=500\exhyphenpenalty=50
    \hangindent 4.1mm\hangafter 1
    \noindent\hbox to 4.1mm{\hss$^{\sixrm\the\fnnumber}$\kern 0.67mm}%
    \vrule width 0pt height 1\baselineskip\egtrm #2}%
    \fi$^{\csname FnN#1\endcsname}\!$}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\title{}

\inst {The ARGUS Collaboration}

\authors {%
 H\:Albrecht,
 A\:A\:Andam,
 U\:Binder,
 P\:B\"{o}kmann,
 G\:Drews,
 H\:Ehrlichmann,
 R\:Gl\"{a}ser,
 T\:Hamacher,
 G\:Harder,
 H\:Hasemann,
 R\:P\:Hofmann,
 H\:Kapitza,
 T\:Kirchhoff,
 A\:Kr\"{u}ger,
 I\:Lembke-Koppitz,
 A\:Nau,
 A\:W\:Nilsson,
 A\:Nippe,
 S\:Nowak\fn{IfH}{DESY, IfH Zeuthen},
 A\:Philipp,
 M\:Reidenbach,
 M\:Sch\"{a}fer,
 H\:Schr\"oder,
 H\:D\:Schulz,
 F\:Sefkow,
 F\:Selonke,
 U\:Volland,
 M\:Walter\fn{IfH}{},
 R\:Wurth,
 A\:Yagil
}
\inst {DESY, Hamburg, Germany}

\authors {%
 R\:D\:Appuhn,
 U\:Buchner,
 J\:P\:Donker,
 A\:Drescher,
 H\:J\:Graf,
 B\:Gr\"{a}we,
 C\:Hast,
 G\:Herrera,
 D\:Kamp,
 H\:Kolanoski,
 A\:Kosche,
 A\:Lange,
 A\:Lindner,
 R\:Mankel,
 A\:Markees,
 U\:Matthiesen,
 H\:Scheck,
 M\:Schieber,
 G\:Schweda,
 T\:Siegmund,
 B\:Spaan,
 H\:Thurn,
 D\:T\"opfer,
 A\:Walther,
 D\:Wegener
 S\:Westerhoff}
\inst {Institut f\"ur Physik\fn{DO}{%
 Supported by the German
 Bundesministerium f\"ur Forschung und Technologie, under contract
 number 054DO51P.},
 Universit\"at Dortmund,
 Germany}

\authors {%
M\:Bittner,
P\:Eckstein,
C\:Frankl,
J\:Graf,
R\:Holtzhauer,
M\:Schmidtler,
M\:Schramm,
K\:R\:Schubert,
R\:Schwierz,
M\:t\"{o}pfer,
R\:Waldi}
\inst{Institut f\"ur Kern- und Teilchenphysik\fn{DR}{%
Supported by the German Bundesministerium f\"ur Forschung
und Technologie, under contract number 055DD11P.},
Technische Universit\"at Dresden, Germany}

\authors {%
 M\:Paulini,
 K\:Reim,
 H\:Wegener}
\inst{Physikalisches Institut\fn{ER}{%
 Supported by the
 German Bundesministerium f\"ur Forschung und Technologie, under
 contract number 054ER12P.}, Universit\"at Erlangen-N\"urnberg,
 Germany}

\authors {%
 o\:Behnke,
 R\:Eckmann,
 M\:Hapke,
 H\:Kuipers,
 O\:Mai,
 R\:Mundt,
 T\:Oest,
 R\:Reiner,
 A\:Rohde,
 W\:Schmidt-Parzefall,
 P\:Weyers}
\inst{II. Institut f\"ur Experimentalphysik, Universit\"at Hamburg,
 Germany}

\authors {%
 U\:Becker,
 C\:Ehmann,
 K\:Fritz,
 W\:Funk,
 F\:Heintz,
 R\:Heller,
 T\:Klinger,
 R\:Salomon,
 B\:Schwingenheuer,
 J\:Stiewe,
 P\:Utzat,
 S\:Werner}
\inst{Institut f\"ur Hochenergiephysik\fn{HD}{%
 Supported by the
 German Bundesministerium f\"ur Forschung und Technologie, under
 contract number 055HD21P.}, Universit\"at Heidelberg, Germany}

\authors {%
 S\:Ball,
 K\:Ehret,
 J\:C\:Gabriel,
 C\:Geyer,
 W\:Hofmann,
 A\:H\"{o}lscher,
 B\:Holzer,
 A\:H\"upper,
 S\:Khan,
 K\:T\:Kn\"opfle,
 M\:Seeger,
 M\:Spahn,
 J\:Spengler}
\inst{Max-Planck-Institut f\"ur Kernphysik, Heidelberg, Germany}

\authors {%
 D\:I\:Britton%
\fn{Mg}{McGill University, Montreal, Quebec, Canada.},
 N\:N\:Brown\fn{Mg}{},
 C\:E\:K\:Charlesworth%\fn{To}{},
\fn{To}{University of Toronto, Toronto, Ontario, Canada.},
 K\:W\:Edwards%
\fn{Ca}{Carleton University, Ottawa, Ontario, Canada.},
 R\:Fernholz\fn{Mg}{},
 W\:Frisken%\fn{Yo}{},
\fn{Yo}{York University, Downsview, Ontario, Canada.},
 C\:Fukunaga\fn{Yo}{},
 D\:J\:Gilkinson\fn{To}{},
 D\:M\:Gingrich\fn{To}{},
 M\:Goddard\fn{Yo}{},
 E\:R\:F\:Hyatt\fn{Mg}{},
 P\:C\:H\:Kim\fn{To}{},
 P\:Krieger\fn{To}{},
 R\:Kutschke\fn{To}{},
 D\:B\:MacFarlane\fn{Mg}{},
 J\:A\:McKenna\fn{To}{},
 K\:W\:McLean\fn{Mg}{},
 R\:S\:Orr\fn{To}{},
 P\:Padley\fn{To}{},
 J\:A\:Parsons\fn{To}{},
 P\:M\:Patel\fn{Mg}{},
 J\:D\:Prentice\fn{To}{},
 P\:R\:B\:Saull\fn{Mg}{},
 S\:C\:Seidel\fn{To}{},
 H\:C\:J\:Seywerd\fn{To}{},
 B\:J\:Stacey\fn{To}{},
 J\:D\:Swain\fn{To}{},
 G\:Tsipolitis\fn{Mg}{},
 K\:Tzamariudaki\fn{Mg}{},
 R\:G\:Van~de~Water\fn{To}{},
 T.-S\:Yoon\fn{To}{},
 J\:C\:Yun\fn{Ca}{}}
\inst {Institute of Particle
 Physics\fn{CDN}{%
 Supported by the Natural Sciences and Engineering
 Research Council, Canada.}, Canada}

\authors {%
 C\:Ratz,
 D\:Re\ss ing,
 T\:Ruf,
 S\:Schael,
 M\:Schneider,
 K\:Strahl,
 J\:Tamminga,
 S\:Weseler}
\inst{Institut f\"ur Experimentelle Kernphysik\fn{KA}{%
 Supported by the
 German Bundesministerium f\"ur Forschung und Technologie, under
 contract number 055KA11P.}, Universit\"at Karlsruhe, Germany}

\authors {%
 B\:Bo\v stjan\v ci\v c,
 G\:Kernel,
 P\:Kri\v zan,
 E\:Kri\v zni\v c,
 M\:Ple\v sko,
 T\:Podobnik,
 T\:\v Zivko
}
\inst{Institut J. Stefan and Oddelek za fiziko\fn{YU}{Supported
 by the Department of Science and Technology of the Republic of
 Slovenia and the Internationales B\"uro KfA,
 J\"ulich.}, Univerza v Ljubljani, Ljubljana, Slovenia}

\authors {%
 H\:I\:Cronstr\"{o}m,
 L\:J\"{o}nsson,
 Y\:Oku}
\inst{Institut of Physics\fn{Sw}{Supported
 by the Swedish Research Council.}, University of Lund, Sweden}

\authors {%
 A\:Arefiev,
 B\:Babaev,
 V\:Balagura,
 S\:Barsuk,
 I\:Belyaev,
 V\:Blinov%
\fn{Nov}{On leave of absence from the Institute of Nuclear Physics, 
Novosibirsk, Russia.},
 S\:Chechelnitsky,
 R\:Chistov,
 M\:Danilov,
 A\:Droutskoy,
 V\:Eiges,
 B\:Fominykh,
 E\:Gerhstein,
 Yu\:Gershtein,
 A\:Golutvin,
 I\:Gorelov,
 O\:Igonkina,
 I\:Korolko,
 G\:Kostina,
 D\:Litvintsev,
 V\:Lubimov,
 V\:Matveev,
 P\:Murat,
 V\:Nagovitsin,
 P\:Pakhlov,
 F\:Ratnikov,
 N\:Root\fn{Nov}{},
 A\:Rostovtsev,
 V\:Ryltsov,
 A\:Semenov,
 S\:Semenov,
 Yu\:Semenov,
 \fbox{V\:Shevchenko},
 V\:Shibaev,
 A\:Snizhko,
 V\:Soloshenko,
 V\:Sopov,
 V\:Tchistilin,
 I\:Tichomirov,
 A\:Undrus\fn{Nov}{},
 Yu\:Zaitsev,
 V\:Zhilich\fn{Nov}{}}
\inst{Institute of Theoretical and Experimental Physics\fn{grn}{Partly
 supported by the International Science Foundation with grants MSB000 and 
MSB300.}
Moscow, Russia}

\authors {%
 R\:Childers,
 C\:W\:Darden,
 H\:Gennow}
\inst{University of South Carolina\fn{DE}{Supported by the U.S.Department of
Energy, under contract DE-AS09-80ER10690.}, Columbia, SC, USA}


\vskip 0pt plus 1fill\eject



%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
